Title of the Master Thesis

### 2015-10-01 Master Thesis/synopsis.tex
Add steps

>>>>

\begin{theorem}[\textit{Pop}]\label{1.1}
Let $K,K'$ be two finitely generated fields of characteristic $0$ and dimension $2$. Suppose there is an isomorphism $\sigma:G_K\to G_{K'}$ between their absolute Galois groups, then there exists a unique field isomorphism $\varphi:\overline{K'}\to\overline{K}$ with $\sigma(g)=\varphi^{-1}g\varphi$ for all $g\in G_K$. In particular $\varphi$ induces a field isomorphism $\varphi:K'\to K$.
\end{theorem}

\begin{step}
There exists a unique group isomorphism $\varphi:K'^\times\to K^\times$ such that for any $P\in X_0$ we have $\varphi(U_{P'})=U_P$ where $P'=\sigma(P)$ and the following diagram:
\[ \begin{tikzcd}
U_{P'} \ar[r, "\varphi"]\ar[d, "r_{P'}"'] & U_P \ar[d, "r_P"]\\
k(P') \ar[r, "\varphi_P"'] & k(P)
\end{tikzcd} \]
\end{step}

\begin{step}
Extending $\varphi$ to a map $K'\to K$ by setting $\varphi(0)=0$ yields a field isomorphism $\varphi:K'\to K$.
\end{step}

\begin{step}
$\varphi$ induces $\sigma:G_K\to G_{K'}$, i.e. $\sigma(g) = \varphi^{-1}g\varphi$ for all $g\in G_K$, and is uniquely determined by this property.
\end{step}
